Limited physiological plasticity and reduced relative variance in physiological rates of ectotherm populations under climate change

### 2024-07-02 ms.qmd
Adding posterior predictions for life history

###########################################################
  # Processing Bayesian Posteriors
###########################################################
      # Create new data for predictions
       lh_b_data <- data.frame(     type = c("acclim", "acute"),
                              max_temp_c = 0,
                             c_accl_time = 0,
                                       V = 0,
                                 habitat = rep(c("t", "m", "f"), each = 4),
                               life.hist = rep(c("j", "a"), each = 2))

@@

        # Contrast statistics
            contrast_lncvr_lh_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
                                                     trait = rep(c("tissue/organism", "biochemical"), each = 1),
                                                    diff = sapply(data.frame(contrast_lncvr_lh_post), mean),
                                                     l95 = sapply(data.frame(contrast_lncvr_lh_post), function(x) quantile(x, 0.025)),
                                                     u95 = sapply(data.frame(contrast_lncvr_lh_post), function(x) quantile(x, 0.975)),
                                                       p = sapply(data.frame(contrast_lncvr_lh_post), function(x) p_value(pmcmc(x))))

>>>>

###########################################################
  # Processing Bayesian Posteriors
###########################################################
      # Create new data for predictions
       lh_b_data <- data.frame(     
                              max_temp_c = 0,
                             c_accl_time = 0,
                                    type = c("acclim", "acute"),
                                 habitat = rep(c("t", "m", "f"), each = 4),
                               life.hist = rep(c("j", "a"), each = 2))

@@

        # Contrast statistics
            contrast_lncvr_lh_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
                                                     trait = rep(c("", ""), each = 1),
                                                    diff = sapply(data.frame(contrast_lncvr_lh_post), mean),
                                                     l95 = sapply(data.frame(contrast_lncvr_lh_post), function(x) quantile(x, 0.025)),
                                                     u95 = sapply(data.frame(contrast_lncvr_lh_post), function(x) quantile(x, 0.975)),
                                                       p = sapply(data.frame(contrast_lncvr_lh_post), function(x) p_value(pmcmc(x))))
